---
title: "Happiness, PISA & Alcohol"
output:
  html_document:
    df_print: paged
    toc: yes
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.height = 7, fig.width = 10)
```
# Introduction

Our project is based on three studies from 2015.
The first one is the ‘World Happiness Report’, which “asks respondents to think of a ladder with the best possible life for them being a 10 and the worst possible life being a 0 and to rate their own current lives on that scale. […] The columns following the happiness score estimate the extent to which each of six factors – economic production, social support, life expectancy, freedom, absence of corruption, and generosity – contribute to making life evaluations higher in each country than they are in Dystopia, […].”

Next is a dataset on the alcohol consumption of people from different countries from the age of 15 and above. Total liters of pure alcohol and different kind of servings, e.g. beer or wine are distinguished.

The last dataset is the PISA – “Program for International Student Assessment” study, which “[…] is applied to 15-year-old students across the world to assess their performance in Math, Reading and Science.”.

Having these three categories and 68 countries to compare, we want to find out, whether there are any correlations between the people’s happiness, school performance and alcohol consumption. Furthermore, we want to give general insights into the datasets by visualizing the data descriptively.

# Setup {.tabset .tabset-fade}

## Install Packages 

-- Install Packages if necessary

```{r eval=TRUE, echo=TRUE}
if(!require(csvread)) install.packages("csvread", repos = "http://cran.us.r-project.org")
if(!require(tidyr)) install.packages("tidyr", repos = "http://cran.us.r-project.org")
if(!require(dplyr)) install.packages("dplyr", repos = "http://cran.us.r-project.org")
if(!require(ggplot2)) install.packages("ggplot2", repos = "http://cran.us.r-project.org")
if(!require(ggthemes)) install.packages("ggthemes",repos = "http://cran.us.r-project.org")
if(!require(corrplot)) install.packages("corrplot", repos = "http://cran.us.r-project.org")
if(!require(knitr)) install.packages("knitr", repos = "http://cran.us.r-project.org")
if(!require(gridExtra)) install.packages("gridExtra", repos = "http://cran.us.r-project.org")
if(!require(maps)) install.packages("maps",repos = "http://cran.us.r-project.org")
if(!require(mapproj)) install.packages("mapproj",repos = "http://cran.us.r-project.org")
```


## Load Libraries

-- Load needed libraries

```{r eval=TRUE, echo=TRUE}
library(csvread)
library(tidyr)
library(dplyr)
library(ggplot2)
library(ggthemes)
library(corrplot)
library(knitr)
library(gridExtra)
library(maps)
```

# Clean Data {.tabset .tabset-fade}

```{r child = 'cleaning/clean_pisa_data.rmd'}
```


```{r child = 'cleaning/clean_happines_data.rmd'}
```


```{r child = 'cleaning/clean_alcohol_data.rmd'}
```


# Merge Data

After reading the cleaned dataset of each study we merged the data by an own developed merge function.  
The data was joined on the "Country"-column and includes data of PISA-Scores 2015, Happiness Record 2015 and its categories and the Acohol consumption of 2015 in pure litres of alcohol for each country that took part in all three studies. In addition to this, we made a minimized Master-Dataset as we do not always need all the data for each analysis.  
  
The final Master-Dataset was saved in a new CSV-file containing  68 Countries with the data of 2015 for the PISA-Study, the GISAH-Study and the World Happiness Record.

```{r child = 'data/Merge_Data.rmd'}
```


# The Data

## Maps

```{r child = 'analysis/descriptive/maps/maps.rmd'}
```

## Regions

```{r child = 'analysis/descriptive/regions/Descriptive_Analysis_regions.rmd'}
```

## Top/Bottom Ten Countries

```{r child = 'analysis/descriptive/top_ten/top_ten.Rmd'}
```

# Analysis

```{r child = 'analysis/regression/Regression_Analysis.rmd'}
```

# Conclusion

In general we can say that happier countries perform better at PISA. Countries with high alcohol consumption are not happier than countries with low alcohol consumption. And students who live in countries with high alcohol consumption perform better at PISA.

It is important to mention, that we cannot explain these correlations. In order to do so, further data and analysis would be needed, for example common influencial factors for PISA performance, alcohol consumption and happiness. Still the insights provided can be a basis for further investigation.

