---
title: "descriptive_analysis"
author: "Cornelius"
date: "1 Juni 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

### Goal

The goal of this file is to provide an overview of the data, by using some descriptive analysis tools.
The Master Data will be used for this.

### Load Librarys

-- Load Library for reading CSV Files.

```{r eval=FALSE, echo=TRUE}
library(csvread)
library(dplyr)
library(ggplot2)
```

### Read raw data

-- Read CSV File "world_happiness_report_2015.csv"  

```{r eval=TRUE, echo=TRUE}
master_data <- read.csv(file = "../../data/master_data/master_data.csv", header = TRUE)
master_data
```

## Descriptive Analysis

### Line charts

To give a first impression, the data of Happiness_Score, PISA_Performance_Mean and Alcohol_Consumption_All_Types will be compared in a line chart, to see tendencies of correlations
```{r eval=TRUE, echo=TRUE}
#Prepare the PISA Score, for comparibility with the other categories, by dividing with 100.

scaled_data <- mutate(master_data, PISA.Performance.Mean=PISA.Performance.Mean/100)
scaled_data
```
```{r eval=TRUE, echo=TRUE}
master.sortedby.happiness = arrange(scaled_data, Happiness.Score)
master.sortedby.happiness

```

```{r eval=TRUE, echo=TRUE}

p1 <- ggplot(data=master.sortedby.happiness, aes(x=Country, y=Happiness.Score, group=1)) +
    geom_line() + geom_point()

p1


'plot(master.sortedby.happiness$Happiness.Score ,type = "o",col = "black", xlab = "country", ylab = "Pisa Score/Happiness Score/Alcohol consumption in liter", ylim=c(0,12))'



```




