---
title: "Descriptive Analysis"
output:
  html_document:
    df_print: paged
    keep_md: yes
---

### Setup

#### Read Data
```{r eval=TRUE, echo=TRUE}
dfData.Master <- read.csv("../data/master_data/master_data.csv")
dfData.Master
```

### Select relevant columns for regional analysis

-- Too many countries for plot analysis, therefore we take the respective regions as categories  

```{r eval=TRUE, echo=TRUE}

dfData.Master.Regions <- select(dfData.Master, -Country, Happiness.Score.Standard.Error)
dfData.Master.Regions 

```


#### Box-Plots {.tabset .tabset-fade}

##### Happines Record

-- How the Happiness Score is made up  

```{r eval=TRUE, echo=TRUE}

theme_set(theme_classic())

pBox.Happiness<- ggplot(dfData.Master.Regions, aes(Region, Happiness.Score))

pBox.Happiness + geom_boxplot(varwidth = T,   fill="plum") +
  theme(axis.text.x = element_text(angle=60, vjust = 0.6, size = 7.5))+
  labs(title="Happiness across Regions",
       x="Region",
       y="Happiness Score")

```

##### Alcohol Consumption

```{r eval=TRUE, echo=TRUE}

theme_set(theme_classic())

pBox.Alcohol<- ggplot(dfData.Master.Regions, aes(Region, Alcohol.Consumption.All.Types))

pBox.Alcohol + geom_boxplot(varwidth = T,   fill="goldenrod2") +
  theme(axis.text.x = element_text(angle=60, vjust = 0.6, size = 7.5))+
  labs(title="Alcohol Consumption across Regions",
       x="Region",
       y="Alcohol Consumption")

```

##### PISA-Study

```{r eval=TRUE, echo=TRUE}

theme_set(theme_classic())

pBox.PISA<- ggplot(dfData.Master.Regions, aes(Region, PISA.Performance.Mean))

pBox.PISA + geom_boxplot(varwidth = T,   fill="aquamarine4") +
  theme(axis.text.x = element_text(angle=60, vjust = 0.6, size = 7.5))+
  labs(title="PISA Performance across Regions",
       x="Region",
       y="PISA Performance")
```

#### Regional Tops {.tabset .tabset-fade}


##### Happiness Record

Preparing the dataset for binning

```{r eval=TRUE, echo=TRUE}
dfData.Master.Happiness<- select(dfData.Master, Region,Happiness.Score, 5:10)
dfData.Master.Happiness<-dfData.Master.Happiness%>%
  group_by(Region)%>%
  summarise_all(funs(mean))

dfData.Master.Happiness

```

```{r eval=TRUE, echo=TRUE}

dfData.bin.Happiness <- gather(dfData.Master.Happiness, Happiness.Reasons, Amount, 3:8 )
dfData.bin.Happiness <- select(dfData.bin.Happiness, Region,Happiness.Reasons, Amount)
dfData.bin.Happiness

```

```{r eval=TRUE, echo=TRUE}

theme_set(theme_classic())

pHappiness.Dodge <- ggplot(dfData.bin.Happiness, aes(Region, Amount))

pHappiness.Dodge + geom_bar(aes(fill=Happiness.Reasons), position = "dodge", stat="identity", color="black")+
  theme(axis.text.x = element_text(angle=70, vjust = 0.6, size = 7.5))+
  scale_fill_brewer(palette="Spectral")+
  labs(title="What's most important for Happiness across Regions",
       x="Region",
       y="Happiness Score")


```

```{r eval=TRUE, echo=TRUE}

theme_set(theme_classic())

pHappiness.Stack <- ggplot(dfData.bin.Happiness, aes(Region, Amount))

pHappiness.Stack + geom_bar(aes(fill=Happiness.Reasons), position = "stack", stat="identity",color="black")+
  theme(axis.text.x = element_text(angle=70, vjust = 0.6, size = 7.5))+
  scale_fill_brewer(palette="Spectral")+
  labs(title="What's most important for Happiness across Regions",
       x="Region",
       y="Happiness Score")

```

##### Alcohol Consumption

```{r eval=TRUE, echo=TRUE}
dfData.Master.Alcohol<- select(dfData.Master, Region, 16:20)

dfData.Master.Alcohol<-dfData.Master.Alcohol%>%
  group_by(Region)%>%
  summarise_all(funs(mean(.,na.rm = TRUE)))

dfData.Master.Alcohol

```

```{r eval=TRUE, echo=TRUE}

dfData.bin.Alcohol <- gather(dfData.Master.Alcohol, Alcohol.Types, Amount, 3:6 )
dfData.bin.Alcohol <- select(dfData.bin.Alcohol, Region,Alcohol.Types, Amount)
dfData.bin.Alcohol

```

```{r eval=TRUE, echo=TRUE}

theme_set(theme_classic())

pAlcohol.Dodge <- ggplot(dfData.bin.Alcohol, aes(Region, Amount))

pAlcohol.Dodge + geom_bar(aes(fill=Alcohol.Types), position ="dodge", stat="identity",color="black")+
  theme(axis.text.x = element_text(angle=70, vjust = 0.6, size = 7.5))+
  scale_fill_brewer(palette="YlOrBr")+
  labs(title="Which alcoholic drinks people drink most across regions",
       x="Region",
       y="Alcohol Consumption")


```

```{r eval=TRUE, echo=TRUE}

theme_set(theme_classic())

pAlcohol.Stack <- ggplot(dfData.bin.Alcohol, aes(Region, Amount))

pAlcohol.Stack + geom_bar(aes(fill=Alcohol.Types), position ="stack", stat="identity",color="black")+
  theme(axis.text.x = element_text(angle=70, vjust = 0.6, size = 7.5))+
  scale_fill_brewer(palette="YlOrBr")+
  labs(title="Which alcoholic drinks people drink most across regions",
       x="Region",
       y="Alcohol Consumption")

```

##### PISA-Study

```{r eval=TRUE, echo=TRUE}
dfData.Master.PISA<- select(dfData.Master, Region, 12:15)

dfData.Master.PISA<-dfData.Master.PISA%>%
  group_by(Region)%>%
  summarise_all(funs(mean(.,na.rm = TRUE)))

dfData.Master.PISA

```

```{r eval=TRUE, echo=TRUE}

dfData.bin.PISA <- gather(dfData.Master.PISA, PISA.Disciplines, Amount, 2:4 )
dfData.bin.PISA<- select(dfData.bin.PISA, Region,PISA.Disciplines, Amount)
dfData.bin.PISA

```

```{r eval=TRUE, echo=TRUE}
theme_set(theme_classic())

pPISA.Dodge<- ggplot(dfData.bin.PISA, aes(Region, Amount))

pPISA.Dodge + geom_bar(aes(fill=PISA.Disciplines), position = "dodge", stat="identity",color="black")+
  theme(axis.text.x = element_text(angle=70, vjust = 0.6, size = 7.5))+
  scale_fill_brewer(palette="Set1")+
  labs(title="What students are best at across regions",
       x="Region",
       y="PISA Performance")


```

```{r eval=TRUE, echo=TRUE}

theme_set(theme_classic())

pPISA.Stack<- ggplot(dfData.bin.PISA, aes(Region, Amount))

pPISA.Stack + geom_bar(aes(fill=PISA.Disciplines), position = "stack", stat="identity",color="black")+
  theme(axis.text.x = element_text(angle=70, vjust = 0.6, size = 7.5))+
  scale_fill_brewer(palette="Set1")+
  labs(title="What students are best at across regions",
       x="Region",
       y="PISA Performance")


```

### 