---
title: "Merge Data"
output:
  html_document:
    df_print: paged
    keep_md: yes
    toc: yes
---
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Setup

### Load Librarys

-- Load Library for reading CSV Files.
-- Load tidyr-library
-- Load dplyr-library

```{r eval=FALSE, echo=TRUE}
library(csvread)
library(tidyr)
library(dplyr)
```


### Read cleaned CSV Files

-- Read CSV File "pisa_data.csv"  
-- Read CSV File "alcohol_data.csv"  
-- Read CSV File "happiness_data.csv"  

```{r eval=TRUE, echo=TRUE}
dfPisa <- read.csv("clean_data/pisa_data.csv")
dfAlcohol <- read.csv("clean_data/alcohol_data.csv")
dfHappiness <- read.csv("clean_data/happiness_data.csv")

dfPisa
dfAlcohol
dfHappiness
```

## Merge and Arrange Data

### Merge Data

-- Load own R-Functions for Multi-Merge  
-- Merge the three Data Sets

```{r eval=TRUE, echo=TRUE}
source("../r/functions.R")
lsData <- list(dfHappiness, dfPisa, dfAlcohol)
dfData <- multiMerge(lsDF = lsData, bFullJoin = FALSE)
dfData
```

### Arrange Data

-- Load own R-Functions for Multi-Merge  
-- Merge the three Data Sets

```{r eval=TRUE, echo=TRUE}
drops <- c(
  "Happiness.Score.Standard.Error",
  "Freedom",
  "Family",
  "Trust.Government.Corruption",
  "Generosity",
  "Dystopia.Residual",
  "Other",
  "Spirits",
  "Wine",
  "Beer"
)
masterData <- dfData[ , !(names(dfData) %in% drops)]
masterData
```

### Save CSV-Files

-- Save CSV-Files

```{r eval=TRUE, echo=TRUE}
write.csv(dfData, file = "master_data/master_data.csv",row.names=FALSE, na="", col.names = TRUE)
write.csv(masterData, file = "master_data/master_data.min.csv",row.names=FALSE, na="", col.names = TRUE)
```


