---
title: "Clean PISA Data"
output:
  html_document:
    df_print: paged
    keep_md: yes
---
## Clean PISA Study

### Introduction

#### Goal

The Goal of this File is to clean the Data of the PISA (Programm for International Student Assessment) study in order  
to use it for comparing with the World Happiness Record and the GISAH Study.
  
The cleaned Data should contain the Scores for the different PISA Scales for the year 2015 in different columns.

### Setup


#### Read PISA - CSV File

-- Read CSV File "pisa_data.csv"  
-- Gets PISA Data for cleaning


```{r eval=TRUE, echo=TRUE}
dfPISA.raw <- read.csv(file = "../data/raw_data/pisa_data.csv", header = TRUE, dec = ".", stringsAsFactors = FALSE)
dfPISA.raw
```

### Clean Data

#### Delete unneccessary columns and rows

-- Delete not needed rows  
-- Rename colums  
-- Delete not needed colums  
  -- Columns with scores for the years 2013 and 2015 are not needed  

```{r eval=TRUE, echo=TRUE}
tail(dfPISA.raw)
n<-dim(dfPISA.raw)[1]
dfPISA.raw<-dfPISA.raw[1:(n-5),]
tail(dfPISA.raw)

names(dfPISA.raw)
names(dfPISA.raw)[1] <- "Country"
names(dfPISA.raw)[5] <- "Score.2013"
names(dfPISA.raw)[6] <- "Score.2014"
names(dfPISA.raw)[7] <- "Score.2015"
names(dfPISA.raw)

drops <- c("Country.Code","Series.Code", "Score.2013", "Score.2014")
dfPISA.raw <- dfPISA.raw[ , !(names(dfPISA.raw) %in% drops)]
head(dfPISA.raw)
```

#### Apart the different PISA-Categorys

-- Apart the Mean Performance of the different Scales 
-- Delete the unneeded "Series.Code"-column  
-- Rename the "Score.2015"-column to the name of the Scale  
-- Free memory by deleting the old dfPISA.raw frame


```{r eval=TRUE, echo=TRUE}
dfPISA.clean <- tidyr::spread(dfPISA.raw, Series.Name, Score.2015)
dfPISA.clean
```

```{r eval=TRUE, echo=TRUE}
dfPISA.raw <- NULL
```

#### Clean data

-- Delete Male and Female Scales as they are not needed when comparing Data Sets for Aclohol Consuption, Happiness Record and PISA Study  
-- Rename Scale Columns  
-- Delete all rows with countries that have not participated in the PISA study  
-- Rename some Countries in order to join the Data Sets later  

```{r eval=TRUE, echo=TRUE}
drops <- c(
  "PISA: Mean performance on the mathematics scale. Female",
  "PISA: Mean performance on the mathematics scale. Male", 
  "PISA: Mean performance on the reading scale. Female", 
  "PISA: Mean performance on the reading scale. Male", 
  "PISA: Mean performance on the science scale. Female", 
  "PISA: Mean performance on the science scale. Male")
dfPISA.clean <- dfPISA.clean[ , !(names(dfPISA.clean) %in% drops)]
```

```{r eval=TRUE, echo=TRUE}
names(dfPISA.clean)[2] <- "PISA.Performance.Mean.Mathematics"
names(dfPISA.clean)[3] <- "PISA.Performance.Mean.Reading"
names(dfPISA.clean)[4] <- "PISA.Performance.Mean.Science"
```

```{r eval=TRUE, echo=TRUE}
dfPISA.clean <- subset(dfPISA.clean, dfPISA.clean[1] != ".." & dfPISA.clean[2] != ".." & dfPISA.clean[3] != ".." & dfPISA.clean[4] != "..")
```

```{r eval=TRUE, echo=TRUE}
ind <- which(dfPISA.clean$Country=="Korea, Rep.", arr.in=TRUE)
dfPISA.clean$Country[ind] <- "South Korea"

ind <- which(dfPISA.clean$Country=="Republic of Korea", arr.in=TRUE)
dfPISA.clean$Country[ind] <- "North Korea"

ind <- which(dfPISA.clean$Country=="Macedonia, FYR", arr.in=TRUE)
dfPISA.clean$Country[ind] <- "Macedonia"

ind <- which(dfPISA.clean$Country=="Slovak Republic", arr.in=TRUE)
dfPISA.clean$Country[ind] <- "Slovakia"

dfPISA.clean
```

#### Calculate PISA Mean Performance

-- Convert Scale-Performance to numeric type  
-- Calculate PISA Mean Performance for every row  
-- Add Value to new column  

```{r eval=TRUE, echo=TRUE}
dfPISA.clean[, c(2,3,4)] <- sapply(dfPISA.clean[, c(2,3,4)], as.numeric)

for (row in 1:nrow(dfPISA.clean)) {
  dfPISA.clean$PISA.Performance.Mean[row] <- (dfPISA.clean$PISA.Performance.Mean.Mathematics[row] + dfPISA.clean$PISA.Performance.Mean.Reading[row] + dfPISA.clean$PISA.Performance.Mean.Science[row]) / 3
}
dfPISA.clean
```

#### Save Data in CSV-File

-- Write the clean PISA-Data to a CSV-File

```{r eval=TRUE, echo=TRUE}
write.csv(dfPISA.clean, file = "../data/clean_data/pisa_data.csv",row.names=FALSE, na="", col.names = TRUE)
```