---
title: "clean_alcohol_data"
output: 
  html_document:
    df_print: paged
    keep_md: yes
---
## Clean GISAH Study

### Goal

tba

### Setup

#### Load Libraries

-- Load Library for reading CSV Files.

```{r eval=FALSE, echo=TRUE}
library(csvread)
library(tidyr)
```

#### Read raw data

```{r eval=TRUE, echo=TRUE}
dfAlcohol.raw <- read.csv(file ="../data/raw_data/alcohol_consumption.csv", header = TRUE)
dfAlcohol.raw


```
Characterisics of raw data  
number of columns:  

```{r eval=TRUE, echo=TRUE}
ncol(dfAlcohol.raw)
```
number of rows:  

```{r eval=TRUE, echo=TRUE}
nrow(dfAlcohol.raw)
```

### Clean raw data
-- Renaming columns  
-- Omit superfluous columns: X1: "Datasource", Years 2016 & 2010-2014

```{r eval=TRUE, echo=TRUE}
names(dfAlcohol.raw)
names(dfAlcohol.raw)[1]<- "Country"
names(dfAlcohol.raw)[2]<- "data_source"
names(dfAlcohol.raw)[3]<- "Beverage_Types"
names(dfAlcohol.raw)[4]<- "Alcohol_per_capita_2016"
names(dfAlcohol.raw)[5]<- "Alcohol_per_capita_2015"
names(dfAlcohol.raw)[6]<- "Alcohol_per_capita_2014"
names(dfAlcohol.raw)[7]<- "Alcohol_per_capita_2013"
names(dfAlcohol.raw)[8]<- "Alcohol_per_capita_2012"
names(dfAlcohol.raw)[9]<- "Alcohol_per_capita_2011"
names(dfAlcohol.raw)[10]<- "Alcohol_per_capita_2010"

drops<- c("data_source","Alcohol_per_capita_2016","Alcohol_per_capita_2014","Alcohol_per_capita_2013","Alcohol_per_capita_2012","Alcohol_per_capita_2011","Alcohol_per_capita_2010")
dfAlcohol.2015 <- dfAlcohol.raw[, !names(dfAlcohol.raw) %in% drops]
dfAlcohol.2015
```

-- Reordering of row/columns: One row for one country, Beverage Types as single columns
```{r eval=TRUE, echo=TRUE}
#delete first row
dfAlcohol.2015<- dfAlcohol.2015[-c(1), ]
dfAlcohol.2015

dfAlcohol.2015 <- dfAlcohol.2015[-c(580:587),]
dfAlcohol.clean <- tidyr::spread(dfAlcohol.2015, Beverage_Types, Alcohol_per_capita_2015, )
dfAlcohol.clean

```
--Renaming Columns

```{r eval=TRUE, echo=TRUE}
names(dfAlcohol.clean)[2] <- "Alcohol.Consumption.All.Types"
names(dfAlcohol.clean)[3] <- "Beer"
names(dfAlcohol.clean)[4] <- "Other"
names(dfAlcohol.clean)[5] <- "Spirits"
names(dfAlcohol.clean)[6] <- "Wine"
names(dfAlcohol.clean)
```

--Renaming Countries

```{r eval=TRUE, echo=TRUE}

ind <- which(levels(dfAlcohol.clean$Country)=="Democratic People's Republic of Korea", arr.in=TRUE)
levels(dfAlcohol.clean$Country)[ind] <- "South Korea"

ind <- which(levels(dfAlcohol.clean$Country)=="Republic of Korea", arr.in=TRUE)
levels(dfAlcohol.clean$Country)[ind] <- "North Korea"

ind <- which(levels(dfAlcohol.clean$Country)=="The former Yugoslav republic of Macedonia", arr.in=TRUE)
levels(dfAlcohol.clean$Country)[ind] <- "Macedonia"

ind <- which(levels(dfAlcohol.clean$Country)=="Czechia", arr.in=TRUE)
levels(dfAlcohol.clean$Country)[ind] <- "Czech Republic"

ind <- which(levels(dfAlcohol.clean$Country)=="Republic of Moldova", arr.in=TRUE)
levels(dfAlcohol.clean$Country)[ind] <- "Moldova"

ind <- which(levels(dfAlcohol.clean$Country)=="United Kingdom of Great Britain and Northern Ireland", arr.in=TRUE)
levels(dfAlcohol.clean$Country)[ind] <- "United Kingdom"

ind <- which(levels(dfAlcohol.clean$Country)=="United States of America", arr.in=TRUE)
levels(dfAlcohol.clean$Country)[ind] <- "United States"

ind <- which(levels(dfAlcohol.clean$Country)=="Viet Nam", arr.in=TRUE)
levels(dfAlcohol.clean$Country)[ind] <- "Vietnam"

```

--Clearing out NAs
```{r eval=TRUE, echo=TRUE}
dfAlcohol.clean <- subset(dfAlcohol.clean, !is.na(dfAlcohol.clean$Alcohol.Consumption.All.Types) & !is.na(dfAlcohol.clean$Beer) & !is.na(dfAlcohol.clean$Beer))
dfAlcohol.clean
```
--Write into CSV

```{r eval=TRUE, echo=TRUE}
write.csv(dfAlcohol.clean, file = "../data/clean_data/alcohol_data.csv",row.names=FALSE, na="", col.names = TRUE)

```
