---
title: "Descriptive Analysis"
output:
  html_document:
    df_print: paged
    keep_md: yes
---

### Setup

#### Read Data
```{r eval=TRUE, echo=TRUE}
dfData.Master <- read.csv("../../../data/master_data/master_data.csv")
dfData.Master
```

### Select relevant columns for regional analysis

-- Too many countries for plot analysis, therefore we take the respective regions as categories  

```{r eval=TRUE, echo=TRUE}

dfData.Master.Regions <- select(dfData.Master, -Country, Happiness.Score.Standard.Error)
dfData.Master.Regions 

```


#### Box-Plots {.tabset .tabset-fade}

##### Happines Record

```{r eval=TRUE, echo=TRUE}

theme_set(theme_classic())

pBox.Happiness<- ggplot(dfData.Master.Regions, aes(Region, Happiness.Score))

pBox.Happiness + geom_boxplot(varwidth = T,   fill="plum") +
  theme(axis.text.x = element_text(angle=60, vjust = 0.6, size = 7.5))+
  labs(title="Happiness across Regions",
       x="Region",
       y="Happiness Score")

```

We can see that people in North America are amongst the happiest, without huge
deviation. That is explained by the fact, that only the USA and Canada accord to North America.
Western Eruope 
Followed by Western Europe, with a bigger deviation, especially some in the lowest 25%, overall deviating
for over two score points.
Middle East and Northern Africa and Central and Eastern Europe also have stronger deviation of over two score points in general,
central and Eastern Europe having the unhappiest country.

##### Alcohol Consumption

```{r eval=TRUE, echo=TRUE}

theme_set(theme_classic())

pBox.Alcohol<- ggplot(dfData.Master.Regions, aes(Region, Alcohol.Consumption.All.Types))

pBox.Alcohol + geom_boxplot(varwidth = T,   fill="goldenrod2") +
  theme(axis.text.x = element_text(angle=60, vjust = 0.6, size = 7.5))+
  labs(title="Alcohol Consumption across Regions",
       x="Region",
       y="Alcohol Consumption")

```

We can see Central and Eastern Europe having the highest deviation of over 10 litres per person and the highest alcohol consuming
countries. Australia and New Zealand, North America and Western Europe have smiliar mean values, with Western Europe having a span of about 5 litres.
In the Middle East, Northern Africa and Southern Asia people tend to drink only little amounts of alcohol. Eastern Asia, Latin America and Caribbean beeing
in the middle of all that.

##### PISA-Study

```{r eval=TRUE, echo=TRUE}

theme_set(theme_classic())

pBox.PISA<- ggplot(dfData.Master.Regions, aes(Region, PISA.Performance.Mean))

pBox.PISA + geom_boxplot(varwidth = T,   fill="aquamarine4") +
  theme(axis.text.x = element_text(angle=60, vjust = 0.6, size = 7.5))+
  labs(title="PISA Performance across Regions",
       x="Region",
       y="PISA Performance")
```

We can see Eastern Asia, Australia and New Zealand, North America and Western Europe with the highest means, leaded by Eastern Asia. Following them we see Central
and Eastern Europe and Southeastern Asia with comparable high spans of up to around 150 points. Lowest countries in this category are from latin America and Caribbean and Middle East and Northern Africa.

#### Regional Tops {.tabset .tabset-fade}


##### Happiness Record

Preparing the dataset for binning

```{r eval=TRUE, echo=TRUE}
dfData.Master.Happiness<- select(dfData.Master, Region,Happiness.Score, 5:10)
dfData.Master.Happiness<-dfData.Master.Happiness%>%
  group_by(Region)%>%
  summarise_all(funs(mean))

dfData.Master.Happiness

```

```{r eval=TRUE, echo=TRUE}

dfData.bin.Happiness <- gather(dfData.Master.Happiness, Happiness.Reasons, Amount, 3:8 )
dfData.bin.Happiness <- select(dfData.bin.Happiness, Region,Happiness.Reasons, Amount)
dfData.bin.Happiness

```

```{r eval=TRUE, echo=TRUE}

theme_set(theme_classic())

pHappiness.Dodge <- ggplot(dfData.bin.Happiness, aes(Region, Amount))

pHappiness.Dodge + geom_bar(aes(fill=Happiness.Reasons), position = "dodge", stat="identity", color="black")+
  theme(axis.text.x = element_text(angle=70, vjust = 0.6, size = 7.5))+
  scale_fill_brewer(palette="Spectral")+
  labs(title="What's most important for Happiness across Regions",
       x="Region",
       y="Happiness Score")


```

```{r eval=TRUE, echo=TRUE}

theme_set(theme_classic())

pHappiness.Stack <- ggplot(dfData.bin.Happiness, aes(Region, Amount))

pHappiness.Stack + geom_bar(aes(fill=Happiness.Reasons), position = "stack", stat="identity",color="black")+
  theme(axis.text.x = element_text(angle=70, vjust = 0.6, size = 7.5))+
  scale_fill_brewer(palette="Spectral")+
  labs(title="What's most important for Happiness across Regions",
       x="Region",
       y="Happiness Score")

```

##### Alcohol Consumption

```{r eval=TRUE, echo=TRUE}
dfData.Master.Alcohol<- select(dfData.Master, Region, 16:20)

dfData.Master.Alcohol<-dfData.Master.Alcohol%>%
  group_by(Region)%>%
  summarise_all(funs(mean(.,na.rm = TRUE)))

dfData.Master.Alcohol

```

```{r eval=TRUE, echo=TRUE}

dfData.bin.Alcohol <- gather(dfData.Master.Alcohol, Alcohol.Types, Amount, 3:6 )
dfData.bin.Alcohol <- select(dfData.bin.Alcohol, Region,Alcohol.Types, Amount)
dfData.bin.Alcohol

```

```{r eval=TRUE, echo=TRUE}

theme_set(theme_classic())

pAlcohol.Dodge <- ggplot(dfData.bin.Alcohol, aes(Region, Amount))

pAlcohol.Dodge + geom_bar(aes(fill=Alcohol.Types), position ="dodge", stat="identity",color="black")+
  theme(axis.text.x = element_text(angle=70, vjust = 0.6, size = 7.5))+
  scale_fill_brewer(palette="YlOrBr")+
  labs(title="Which alcoholic drinks people drink most across regions",
       x="Region",
       y="Alcohol Consumption")


```

```{r eval=TRUE, echo=TRUE}

theme_set(theme_classic())

pAlcohol.Stack <- ggplot(dfData.bin.Alcohol, aes(Region, Amount))

pAlcohol.Stack + geom_bar(aes(fill=Alcohol.Types), position ="stack", stat="identity",color="black")+
  theme(axis.text.x = element_text(angle=70, vjust = 0.6, size = 7.5))+
  scale_fill_brewer(palette="YlOrBr")+
  labs(title="Which alcoholic drinks people drink most across regions",
       x="Region",
       y="Alcohol Consumption")

```

##### PISA-Study

```{r eval=TRUE, echo=TRUE}
dfData.Master.PISA<- select(dfData.Master, Region, 12:15)

dfData.Master.PISA<-dfData.Master.PISA%>%
  group_by(Region)%>%
  summarise_all(funs(mean(.,na.rm = TRUE)))

dfData.Master.PISA

```

```{r eval=TRUE, echo=TRUE}

dfData.bin.PISA <- gather(dfData.Master.PISA, PISA.Disciplines, Amount, 2:4 )
dfData.bin.PISA<- select(dfData.bin.PISA, Region,PISA.Disciplines, Amount)
dfData.bin.PISA

```

```{r eval=TRUE, echo=TRUE}
theme_set(theme_classic())

pPISA.Dodge<- ggplot(dfData.bin.PISA, aes(Region, Amount))

pPISA.Dodge + geom_bar(aes(fill=PISA.Disciplines), position = "dodge", stat="identity",color="black")+
  theme(axis.text.x = element_text(angle=70, vjust = 0.6, size = 7.5))+
  scale_fill_brewer(palette="Set1")+
  labs(title="What students are best at across regions",
       x="Region",
       y="PISA Performance")


```

```{r eval=TRUE, echo=TRUE}

theme_set(theme_classic())

pPISA.Stack<- ggplot(dfData.bin.PISA, aes(Region, Amount))

pPISA.Stack + geom_bar(aes(fill=PISA.Disciplines), position = "stack", stat="identity",color="black")+
  theme(axis.text.x = element_text(angle=70, vjust = 0.6, size = 7.5))+
  scale_fill_brewer(palette="Set1")+
  labs(title="What students are best at across regions",
       x="Region",
       y="PISA Performance")


```

### 