---
title: "Descriptive Maps"
output:
  html_document:
    df_print: paged
    keep_md: yes
---


### Setup

#### Load Data from CSV

-- Load CSVf- files

```{r eval=TRUE, echo=TRUE}
dfData.PISA <- read.csv("../../../data/clean_data/pisa_data.csv", stringsAsFactors = FALSE)
dfData.Alcohol <- read.csv("../../../data/clean_data/alcohol_data.csv", stringsAsFactors = FALSE)
dfData.Happiness <- read.csv("../../../data/clean_data/happiness_data.csv", stringsAsFactors = FALSE)
```

### Adapt Data

#### Adapt Data to ggplot2-World Map {.tabset .tabset-fade}

##### World Data

```{r eval=TRUE, echo=TRUE}
dfData.World <- ggplot2::map_data('world')
dfData.World <- dplyr::filter(dfData.World, region != "Antarctica")
dfData.World <- ggplot2::fortify(dfData.World)

ind <- which(dfData.World$region=="Trinidad", arr.in=TRUE)
for (country in ind) {
  dfData.World$region[ind] <- "Trinidad and Tobago"
}
ind <- which(dfData.World$region=="Tobago", arr.in=TRUE)
for (country in ind) {
  dfData.World$region[ind] <- "Trinidad and Tobago"
}
dfData.World
```

##### Alcohol Study

```{r eval=TRUE, echo=TRUE}
dfData.Alcohol
names(dfData.Alcohol)[1] <- "region"
ind <- which(dfData.Alcohol$region=="Russian Federation", arr.in=TRUE)
dfData.Alcohol$region[ind] <- "Russia"
ind <- which(dfData.Alcohol$region=="United Kingdom", arr.in=TRUE)
dfData.Alcohol$region[ind] <- "UK"
ind <- which(dfData.Alcohol$region=="United States", arr.in=TRUE)
dfData.Alcohol$region[ind] <- "USA"
dfData.Alcohol
```

##### Happiness Record

```{r eval=TRUE, echo=TRUE}
names(dfData.Happiness)[1] <- "region"
ind <- which(dfData.Happiness$region=="Russian Federation", arr.in=TRUE)
dfData.Happiness$region[ind] <- "Russia"
ind <- which(dfData.Happiness$region=="United Kingdom", arr.in=TRUE)
dfData.Happiness$region[ind] <- "UK"
ind <- which(dfData.Happiness$region=="United States", arr.in=TRUE)
dfData.Happiness$region[ind] <- "USA"
dfData.Happiness
```

##### PISA-Study

```{r eval=TRUE, echo=TRUE}
names(dfData.PISA)[1] <- "region"
ind <- which(dfData.PISA$region=="Russian Federation", arr.in=TRUE)
dfData.PISA$region[ind] <- "Russia"
ind <- which(dfData.PISA$region=="United Kingdom", arr.in=TRUE)
dfData.PISA$region[ind] <- "UK"
ind <- which(dfData.PISA$region=="United States", arr.in=TRUE)
dfData.PISA$region[ind] <- "USA"
dfData.PISA
```

####

### Create Maps {.tabset .tabset-fade}

#### World´s Alcohol consumption

-- Displays the World´s Alcohol Consumption in pure litres of Alcohol  
-- White countries have not participated in the study  

```{r eval=TRUE, echo=TRUE}
df <- data.frame(region=dfData.Alcohol$region, 
                 value=dfData.Alcohol$Alcohol.Consumption.All.Types, 
                 stringsAsFactors=FALSE)

p <- ggplot2::ggplot()
p <- p + ggplot2::geom_map(data=dfData.World, map=dfData.World,
                  ggplot2::aes(x=long, y=lat, group=group, map_id=region),
                  fill="white", colour="#7f7f7f", size=0.3)
p <- p + ggplot2::geom_map(data=df, map=dfData.World,
                  ggplot2::aes(fill=value, map_id=region),
                  colour="#7f7f7f", size=0.3)
p <- p + ggplot2::coord_map("rectangular", lat0=0, xlim=c(-180,180), ylim=c(-60, 90))
p <- p + ggplot2::scale_fill_continuous(low="grey", high="blue", 
                               guide="colorbar")
p <- p + ggplot2::scale_y_continuous(breaks=c())
p <- p + ggplot2::scale_x_continuous(breaks=c())
p <- p + ggplot2::labs(fill="Litres", title="Litres of pure Alcohol per Capita in 2015", x="Latitude", y="Longitude")
p <- p + ggplot2::theme_bw()
p <- p + ggplot2::theme(panel.border = ggplot2::element_blank())
p
```

#### World´s Happiness Record

-- Displays the World´s Happiness record  
-- White countries have not participated in the study  

```{r eval=TRUE, echo=TRUE}
df <- data.frame(region=dfData.Happiness$region, 
                 value=dfData.Happiness$Happiness.Score, 
                 stringsAsFactors=FALSE)

p <- ggplot2::ggplot()
p <- p + ggplot2::geom_map(data=dfData.World, map=dfData.World,
                  ggplot2::aes(x=long, y=lat, group=group, map_id=region),
                  fill="white", colour="#7f7f7f", size=0.3)
p <- p + ggplot2::geom_map(data=df, map=dfData.World,
                  ggplot2::aes(fill=value, map_id=region),
                  colour="#7f7f7f", size=0.3)
p <- p + ggplot2::coord_map("rectangular", lat0=0, xlim=c(-180,180), ylim=c(-60, 90))
p <- p + ggplot2::scale_fill_continuous(low="red", high="green", 
                               guide="colorbar")
p <- p + ggplot2::scale_y_continuous(breaks=c())
p <- p + ggplot2::scale_x_continuous(breaks=c())
p <- p + ggplot2::labs(fill="Happiness Score", title="Happiness Score 2015", x="Latitude", y="Longitude")
p <- p + ggplot2::theme_bw()
p <- p + ggplot2::theme(panel.border = ggplot2::element_blank())
p
```

#### PISA-Study Map

-- Displays Mean Performance of the PISA-Study  
-- White countries have not participated in the study  

```{r eval=TRUE, echo=TRUE}
df <- data.frame(region=dfData.PISA$region, 
                 value=dfData.PISA$PISA.Performance.Mean, 
                 stringsAsFactors=FALSE)

p <- ggplot2::ggplot()
p <- p + ggplot2::geom_map(data=dfData.World, map=dfData.World,
                  ggplot2::aes(x=long, y=lat, group=group, map_id=region),
                  fill="white", colour="#7f7f7f", size=0.3)
p <- p + ggplot2::geom_map(data=df, map=dfData.World,
                  ggplot2::aes(fill=value, map_id=region),
                  colour="#7f7f7f", size=0.3)
p <- p + ggplot2::coord_map("rectangular", lat0=0, xlim=c(-180,180), ylim=c(-60, 90))
p <- p + ggplot2::scale_fill_continuous(low="grey", high="blue", 
                               guide="colorbar")
p <- p + ggplot2::scale_y_continuous(breaks=c())
p <- p + ggplot2::scale_x_continuous(breaks=c())
p <- p + ggplot2::labs(fill="Mean Performance Score", title="Mean PISA Performance in 2015", x="Latitude", y="Longitude")
p <- p + ggplot2::theme_bw()
p <- p + ggplot2::theme(panel.border = ggplot2::element_blank())
p
```